\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\familydefault}{\sfdefault}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section Formatting
\titleformat{\section}{
  \vspace{-5pt}\sffamily\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection Formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure the generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

\begin{document}

% -------------------- HEADING--------------------
\vspace{-7pt}

\begin{center}
  \textbf{\Huge \scshape Tomas Oh} \\ \vspace{4pt}
  \small
  \faIcon{envelope}
  \href{mailto:tomasohe@csu.fullerton.edu}
  {\underline{tomasoh@csu.fullerton.edu}}
  \faIcon{linkedin}
  \href{https://www.linkedin.com/in/tomaasoh/}{\underline{www.linkedin.com/in/tomaasoh/}}
  \faIcon{github}
  \href{https://github.com/tomasohCHOM}{\underline{github.com/tomasohCHOM}}
  \faIcon{home}
  {Orange County, CA}
\end{center}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{California State University, Fullerton}{Expected Graduation: December 2025}
{Bachelor of Science in Computer Science, Minor in Mathematics}{GPA: 3.95/4.0}
% \vspace{-5pt}
\resumeItem
{\textbf{Relevant Coursework:} OOP, Data Structures, Software Engineering, Operating Systems, Web Back-End Engineering} \\
\resumeSubHeadingListEnd

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Web Development Team Lead} $|$
  \footnotesize\emph{FullyHacks 2025}}{July 2024 -- Present}
\resumeItemListStart
\resumeItem{Led a team of seven to build the website for CSUF's largest 24-hour hackathon (\textbf{400+} applicants, \textbf{10} sponsors in 2024).}
\resumeItem{Developed the website with \textbf{Next.js}, \textbf{React}, and \textbf{TypeScript}, storing and managing applicant data in \textbf{MongoDB}.}
\resumeItem{Conducted weekly meetings, delegated tasks effectively, and implemented CI/CD pipelines to optimize project workflows.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Data Science and AI/Robotics Research Assistant} $|$
  \footnotesize\emph{Project ACCESS at CSUF}}{June 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Completed a ten-week research program, collaborating with a team of three to build projects addressing social justice issues.}
\resumeItem{Implemented fall-detection and emergency alerting functionalities for a \textbf{Raspberry PI 5} Robot Car, utilizing YOLO v8 pose-detection model, SQLite to store owner information, and SMTB for text messaging.}
\resumeItem{Developed a machine learning model to predict salaries in the technology industry based on demographic data, using NumPy, Pandas, and scikit-learn and \textbf{70,000+} responses from the Stack Overflow 2022 Developer Survey.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Supplemental Instruction Leader} $|$
  \footnotesize\emph{California State University, Fullerton}}{Jan 2024 -- Present}
\resumeItemListStart
\resumeItem{Conducted weekly sessions to reinforce students' understanding of \textbf{multivariable} and \textbf{vector calculus} concepts.}
\resumeItem{Integrated interactive and collaborative study techniques to help improve problem-solving skills for complex topics.}
\resumeItem{Fostered active participation and peer discussion with \textbf{30+} students, ultimately increasing average student grades by \textbf{10\%}.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% PROJECTS
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{vimaroo} $|$ \emph{SvelteKit, TypeScript, TailwindCSS, Supabase, Monaco, Vim}}{\footnotesize\faIcon{github} \href{https://github.com/tomasohCHOM/vimaroo}{tomasohCHOM/vimaroo}}
\resumeItemListStart
\resumeItem{Built a web application that allows users to practice \textbf{Vim} keybindings, featuring interactive, motion-focused tests.}
\resumeItem{Implemented authentication, user management, and real-time statistics tracking using Supabase and PostgreSQL.}
\resumeItem{Achieved community recognition with \textbf{30+} GitHub stars and \textbf{100+} upvotes on the Vim and Neovim subreddits.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{aoc-dailies} $|$ \emph{Deno, TypeScript, Discord REST, Advent Of Code}}{\footnotesize\faIcon{github} \href{https://github.com/tomasohCHOM/aoc-dailies}{tomasohCHOM/aoc-dailies}}
\resumeItemListStart
\resumeItem{Created a Discord webhook to send Advent Of Code daily challenge notifications for \textbf{100+} active participants.}
\resumeItem{Set up cron jobs with retry promises to scrape daily challenges information and deliver them via Discord embed messages.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{go-blueprint} $|$ \emph{Go, Cobra CLI, Docker, Vite}}{\footnotesize\faIcon{github} \href{https://github.com/Melkeydev/go-blueprint}{Melkeydev/go-blueprint}}
\resumeItemListStart
\resumeItem{Contributed to an open source CLI tool that spins up Go projects with popular frameworks (\textbf{4.700+} GitHub stars).}
\resumeItem{Implemented a flag that allows users to opt out from creating a git repository, resolving \textbf{16\%} of reported bugs.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% SKILLS
\section{Skills}
\begin{itemize}[leftmargin=0.1in, label={}]
  \small{\item{
    \textbf{Programming}{: C, C++, Python, TypeScript/JavaScript, Go, Java, Rust, HTML/CSS, SQL} \\
    \textbf{Web Development}{: Node.js, Express, Next.js, ReactJS, SvelteKit, Flask, FastAPI, TailwindCSS} \\
    \textbf{Databases \& Cloud}{: PostgreSQL, SQLite, MongoDB, Supabase, Firebase, AWS, Docker, Redis} \\
    \textbf{Tools}{: Git, Bash, Linux, Vim/Neovim, REST APIs, CI/CD, Jupyter Notebook, Postman, MS Office}
 }}
\end{itemize}

% LEADERSHIP
\section{Leadership}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Open Source Software Team Lead} $|$
  \footnotesize\emph{Association for Computing Machinery (ACM)}}{Aug 2024 -- Present}
\resumeItemListStart
\resumeItem{Led an \textbf{open-source software} initiative within CSUF's largest computer science club, consisting of \textbf{60+} contributors.}
\resumeItem{Worked with team members to develop \textbf{20+} open-source projects, fostering skill development and hands-on collaboration.}
\resumeItem{Advanced weekly workshops focused on open-source development, incorporating interactive sessions and guest talks by open-source maintainers, resulting in a \textbf{50\%} increase of attendees compared to previous years.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}

